Manuscript 1 code

### 2025-01-28 manuscript_1_code.Rmd
added initial area model at quad level

#merge Noam's data with functional group summary 
alpha_diversity_quad_macro <- merge(alpha_diversity_quad_macro,
                                    fg_summary_wide[,c("location", "year", "site",  "habitat", "functional_richness")],
                                    by = c("location", "year", "site", "habitat"))

@@

```{r mean plot level adiv}
mean_adiv_quad <- alpha_diversity_quad_macro %>% 
  dplyr::group_by(year, habitat, site) %>% 
  dplyr::summarise(
    richness_mean = mean(richness, na.rm = T),
    functional_richness_mean = mean(functional_richness, na.rm = T),
    cover_mean = mean(macroalgal_prop_cover, na.rm = T))

@@

>>>>

#merge Noam's data with functional group summary 
alpha_diversity_quad_macro <- merge(alpha_diversity_quad_macro,
                                    fg_summary_wide[,c("location", "year", "site",  "habitat", "functional_richness")],
                                    by = c("location", "year", "site", "habitat"))
# add small amount to avoid 0s in data for gamma modeling
alpha_diversity_quad_macro$area_trans <- alpha_diversity_quad_macro$area + 10E-10

@@

```{r mean plot level adiv}
mean_adiv_quad <- alpha_diversity_quad_macro %>% 
  dplyr::group_by(year, habitat, site) %>% 
  dplyr::summarise(
    richness_mean = mean(richness, na.rm = T),
    functional_richness_mean = mean(functional_richness, na.rm = T),
    cover_mean = mean(macroalgal_prop_cover, na.rm = T),
    area_mean = mean(area_trans, na.rm = T))

@@

# area model - play around with area vs. area_trans
area_mod <- glmmTMB(area ~ richness*habitat + (1|site/location) + (1|year), family = ziGamma("log"), ziformula = ~1, data = alpha_diversity_quad_macro)
summary(area_mod)
Anova(area_mod)
hist(residuals(area_mod))
plot(simulateResiduals(area_mod))
plot(residuals(area_mod) ~ fitted(area_mod)) # heteroskedastic - because of the few 100% cover plots?
r.squaredGLMM(area_mod) # 0.631, 0.650
performance::r2(area_mod) # 0.635, 0.654
emtrends(area_mod, pairwise ~ habitat, var = "richness")
